---
title: "relation2"
author: "xinru cheng"
date: "10/26/2018"
output: html_document
---


```{r}
com_call<-filter(raa.data)%>%select(ï..ID,CallType)
com_call<-cbind.data.frame(com_call,chiefc[,2])
colnames(com_call)<-c('id','Calltype','ChiefComplaint')
length(unique(com_call[,3]))
simp_com<-matrix(NA,nrow=nrow(raa.data),ncol=1)
for (i in 1:nrow(simp_com)){
  simp_com[i,1]<-strsplit(toString(com_call[i,3]),'-')[[1]][1]
} 
length(unique(simp_com[,1]))
com_call<-cbind.data.frame(com_call,simp_com)
colnames(com_call)<-c('id','Calltype','ChiefComplaint','SimpleComplaint')
head(com_call)
```
create a dataframe including Simple complaint and impression and intervention
```{r}
com_im_int<-cbind.data.frame(simp_com,raa.data$ï..ID,raa.data$Impression,raa.data$Interventions)
```

draw plot to show complaint distribution
```{r}
complaint<-as.data.frame(table(simp_com)) #count the number of distinct calltype
comp<-as.matrix(complaint)
colnames(comp)<-c('complaint','frequency')
comp<-comp[order(ct[,2],decreasing = 'True'),] #sort call type in decreasing order
comp<-as.data.frame(comp)
comp$complaint <- factor(comp$complaint, levels = comp$complaint[order(comp$frequency)])
ggplot(comp)+
  theme(axis.text.x=element_text(angle=60,hjust = 1))+
  geom_bar(aes(x=complaint,y=frequency),stat='identity')+
  ggtitle("distribution of complaint")+
  xlab("complaint")+
  ylab("Number")
```





create map between calltype and simplified complaint
```{r}
cal_com<-list()
keys=list()
values=list()
for (i in 1:nrow(raa.data)){
  key<-com_call[i,2]  #Calltype is key
  value<-as.character(m[i,4])  #Complaint is value
  for (j in 5:ncol(com_call)){
       value<-c(value,as.character(com_call[i,j]))
    
  }
  if (key %in% keys){
    a<-c(cal_com[[key]],value)
    cal_com[[key]]<-a
  }
  else {
    cal_com[[key]]<-value
    keys<-c(keys,key)
  }
}

table(cal_com[1]))
head(com_call)
cal_com
```

get unique value of complaint and calltype
```{r}
call_unique<-unique(com_call$Calltype)
call_unique
length(call_unique)
com_unique<-unique(com_call$SimpleComplaint)
com_unique
length(com_unique)
```

ceate df with calltype as row and complaint as columns
```{r}
calcom_df<-matrix(NA, nrow=27, ncol=30)
colnames(calcom_df)<-(com_unique)
rownames(calcom_df)<-(call_unique)
for (i in 1:27){
  a<-cal_com[[i]]
  for (j in 1:length(com_unique)){
    num<-length(which(a==com_unique[j]))
    #perc<-num/length(a)
    calcom_df[i,j]<-num
  }
}
head(calcom_df)

heatmap(calcom_df)
```

```{r}
cmost<-matrix(NA,nrow=27,ncol = 2)
colnames(cmost)<-c('calltype','complaint')
com_unique
cmost[,1]<-call_unique
for (i in 1: nrow(cmost)){
  m=max(calcom_df[i,])
  for (j in 1: ncol(calcom_df)){
    if (calcom_df[i,j]==m){
    cmost[i,2]<-toString(com_unique[j])
    }
  }
} 
cmost
heatmap(cmost[,1])
#p1<-ggparcoord(cmost, columns = c(1,2), scale = 'globalminmax')
#my.pca <- prcomp(cmost,retx=TRUE,center=FALSE, scale=FALSE)
```
a matrix that only includes id, impression and intervention
```{r}
all_im_int<-raa.data[,c(1,5,7)] #a matrix that only includes id, impression and intervention
imp_inter3<-matrix(NA,nrow=nrow(all_im_int),ncol=2)
colnames(imp_inter3)<-c('id','impression')
for (i in 1: nrow(imp_inter3)){
  id<-as.character(all_im_int$ï..ID[i])
  imp_inter3[i,1]<-id
}

for (i in 1:nrow(all_im_int)){
  v<-as.character(all_im_int$Impression[i])
  v<-(strsplit(v,'}')[[1]])[1]#take the last element as suggested by Sile
  v<-gsub('\\{','',v)
  imp_inter3[i,2]<-v
}                                  #extract the first element of chief complaint column

imp_inter3 <- transform(as.data.frame(imp_inter3),inter_n=as.numeric(factor(impression))) #transform chiefcom to unique numeric value 
head(imp_inter3)
max(imp_inter2[,3])
head(all_im_int)
```
```{r}
id3<-as.matrix(imp_inter3[,1])
m3<-cbind(id3,matrix(NA, nrow=nrow(imp_inter3),ncol=12))
#colnames(m3)<-c('id','v1','v2','v3','v4','v5','v6','v7','v8','v9','v10','v11','v12','v13','v14','v15','v16','v17','v18','v19')
for (i in 1:nrow(all_im_int)){
  v<-as.character(all_im_int$Interventions[i])
  v<-gsub('\\{','',v)
  v<-strsplit(v,'}')[[1]]
  v<-gsub("\\{", "",v)
  v<-gsub('.*:','',v)
  v<-trimws(v)
  for (j in (1:length(v))){
    j2<-j+1
    m3[i,j2]<-v[j]
  }
} 
m3<-cbind(imp_inter3,m3)
m3
m3<-m3[,-4]
m3
max(m2[,3])
head(m)
head(all_im_int)
```

```{r}
dic_all<-list()
keys4=list()
values4=list()
for (i in 1:nrow(all_im_int)){
  key<-as.character(m[i,2])
  value<-as.character(m[i,4])
  for (j in 5:ncol(m)){
    if (!is.na(m[i,j])){
       value<-c(value,as.character(m[i,j]))
    }
  }
  if (key %in% keys4){
    a<-c(dic_all[[key]],value)
    dic_all[[key]]<-a
  }
  else {
    dic_all[[key]]<-value
    keys4<-c(keys,key)
  }
}
dic_all
table(dic_all[1])
length(dic_all)
```

```{r}
intervention_all=c()
for (i in 1:nrow(m)){
  for (j in 4: ncol(m)){
    if (!is.na(m[i,j])){
      intervention_all<-c(intervention_all,as.character(m[i,j]))
    }
  }
} 
length(unique(intervention_all))
intervention4<-unique(intervention_all)
intervention4
```
```{r}
all_inter<-matrix(NA, nrow=92, ncol=52)
length(intervention4)
intervention4<-intervention4[-c(1,3)]
length(intervention4)
colnames(all_inter)<-(intervention4)
im_v<-unique(m[,2])
rownames(all_inter)<-im_v

#impression_v[2]
#dic_breath[[impression_v[2]]]
for (i in 1:92){
  indi_inter4<-dic_all[[im_v[i]]]
  for (j in 1:length(intervention4)){
    num<-length(which(indi_inter4==intervention4[j]))
    perc<-num/length(indi_inter4)
    all_inter[i,j]<-perc
  }
}

heatmap(all_inter)
head(all_inter)
```
 find the intervention with the max possibility for each impression
```{r}

```
 
 